---
title: "Scheduling a QA_QC job for connect"
output:
  html_document:
    df_print: paged
---

This assumes you have a  GCP account and appropriate permissions to the R dev/stage/prod environments

make sure you have GoogleCloudRunner installed...

First, Let's define some GCP Project related information: You will need to set this appropriately  Then you will need the oauth2 from the QAQC service account

The JSON file pointed to by the variable *oauth_client_id_file* contain the client id/secret for project.  Note: this MUST be a desktop application...
The other JSON file in gar_auth_service is the service account 
see [Mark Edmonodson's GCP setup page for more details](https://code.markedmondson.me/googleCloudRunner/articles/setup-gcp.html) particularly step 5.
We wont set it up in the Renviornment, because we want to be able to switch between projects.
```{r}
library(googleCloudRunner)
library(googleAuthR)

cr_project_set("nih-nci-dceg-druss")
cr_bucket_set("nih-nci-dceg-druss-bucket1")
cr_region_set("us-east1")
my_gcs_bucket <- "gs://nih-nci-dceg-druss-bucket1"

oauth_client_id_file <- "~/.gcpkeys/TestOAuthWithR.json"
token <- gar_auth_service("~/.gcpkeys/druss-cloud-build-R.json",
                          scope = "https://www.googleapis.com/auth/cloud-platform")
cr_email_set(token$secrets$client_email)
```



first lets deploy raw R code..  
```{r}
cr_deploy_r("myScripts/script1.R")
```
Note: that this build first pulls the rocker/latest from the default docker repository, builds the container, then runs the container.  The process takes over a minute to run a script that takes less than 0.2 sec on my mac laptop 

By the way, you can have each R command as separate entry in a vector...
```{r}
r_code <- c("list.files()","sessionInfo()")
cr_deploy_r(r_code)
```

You can schedule to run a job at 20 minutes after the hour..
```{r}
cr_deploy_r("myScripts/script1.R",schedule = '20 * * * *')
```


I moved the rocker/r-ver:4.1.0 from the docker repo to a gcp.  On my laptop I ran the commmands below.  I also tested, you can run the commands in google cloud shell, so you dont need to install docker.
```
docker pull rocker/r-ver:4.1.0
docker tag rocker/r-ver:4.1.0  us.gcr.io/nih-nci-dceg-druss/r-ver:4.1.0
docker push  us.gcr.io/nih-nci-dceg-druss/r-ver:4.1.0
```



lets try to run using the image in gcp's container registry 
```{r}

bs <- cr_buildstep_r(
    "myScripts/script1.R",
    prefix = "",
    name = "us.gcr.io/nih-nci-dceg-druss/r-ver:4.1.0"
  )
my_build <- cr_build_yaml(bs, timeout = 2400)
cr_build(my_build)
```
This took about 20 seconds.


```{r}
cr_deploy_r("myScripts/script1.R",
            schedule = '20 * * * *',
            run_name = 'daniels-test-script',
            r_image = "us.gcr.io/nih-nci-dceg-druss/r-ver:4.1.0",prefix="")
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

